Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-14 article.tex
Mise en boite des illustrations

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/points.png}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_pts}
\end{figure}

\begin{figure}[!b]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/distance_elim.png}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_dis}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/angle_elim.png}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_ang}
\end{figure}

\begin{figure}[!b]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_qua}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/neighs.png}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_nei}
\end{figure}

>>>>

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/points.png}}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_pts}
\end{figure}

\begin{figure}[!b]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/distance_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_dis}
\end{figure}

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/angle_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_ang}
\end{figure}

\begin{figure}[!b]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_qua}
\end{figure}

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/neighs.png}}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_nei}
\end{figure}
